---
title: "Operating ArchaeoSRP"
author: "Sean M. Bergin and Grant Snitker"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Operating ArchaeoSRP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
  
  library(magrittr)
  library(kableExtra)

```

This vignette demonstrates how to utilize the ArchaeoSRP package for creating machine-readable pdfs of site forms and extracting pertinent information about the recorded each archaeological site form for research or management applications. More information on the design, installation, and functionality of [ArchaeoSRP](https://github.com/seanbergin/archaeosrp) can be found in the Readme and supporting documents on GitHub. 

## Load required packages
```{r install, include = T}
library(remotes)
```

## Install ArchaeoSRP from GitHub
```{r install ArchaeoSRP, include = T, message=FALSE, results = FALSE}
remotes::install_github("seanbergin/archaeosrp", force = TRUE)
library(ArchaeoSRP)
```

## Assign the example PDF location to a variable
```{r example pdf, include = T}
pdflocation <- system.file("extdata", "SamplePDFs", package = "ArchaeoSRP", mustWork = TRUE)
```
## Use ArchaeSRP to scan the documents and extract information
```{r scan extract, include = T}
siteDF <- processPDFDirectory(pdflocation)

```
## Display results dataframe 
```{r Display results}
knitr::kable(siteDF, format = "html", table.attr = "style='width:30%;'") %>%
  kableExtra::kable_styling()
kable(siteDF, table.attr = "style='width:40%;'" ) %>% kable_classic(full_width = T, position = "center", )

siteDF %>% kable("html") %>%
  kable_styling(font_size = 9)
```
```
